Deep Neural Network for Nuclei Segmentation in Histopathology images

### 2016-11-06 Paper.tex
last day

\section{Related work}
\label{sec:related}

Talk about related work.
Recent work in deep learning for segmentation, histopathology analysis helped by images. Maybe not too much as the paper is small..
\section{DataSet}
\label{sec:dataset}

%% Contribution as a dataset, small introduction
One of the main contributions of this paper is the now public available 
nuclei detection dataset within HE stainned histopathology images which 
can be found at www.cbio.ensmp.fr:/pnaylor/download/dataset.zip (not 
a true address). This annotated dataset provides images clustered by 
patients. Each patient has at least 3 annotated $512 \times 512$ HE 
stainned histopathology images with their associated ground truth. Each 
ground truth image is a $512 \times 512$ where each pixel value above 
$0$ is considered as a pixel belonging to a nuclei. The differences in 
values of these pixels denote different nucleus, such an annotation can 
be used in several processing step which does or doesn't take into 
account clutered nuclei. See figure \ref{fig:annotation} for an example of 
three annotated images. This annotation was conducted via the help of 
the software ITK-snap and were annotated by the authors of the paper.

@@

%%Data set description 
We can describe the dataset provided.

@@

%% Data augmentation and Hyper parameter training: Training scheme
%% Check number of images and number of transformations
To train our models, as the number of available annotated is scarse, we 
used a great number of transformation for the data augmentation. From 
a original size of 33 annotated images, adding flips, rotations, bluriness 
and random elastic deformations enabled us to have more then 
$400 000$ training images per patient. 
We also try out several hyperparameter configurations: the learning rate and 
momentum for the stochastic gradient descent, the weight decay value.  
In practice, we found that hyperparameters tuning didn't influence the 
scores much, the exepction being the learning rate. If the learning rate 
was not of the right magnitude the given network did not seem to learn. 
We also experienced with different 
initialization value and if possible, we also considered pretrained layers. 
Using pretrained layers made learning more efficient and made score 
values more robust.

\section{Different architectures/Results}
\label{sec:method}
We experience with 4 know arhitectures in semantic segmentation, one 
will be named BaochuanNet, Fully Convolutionnal Net (FCN), DeconvNet, 
UNet. The most basic architecture, BaochuanNet, consists of 4 
convolutionnal layer where each convolutionnal layer has 8 feature map. 
This net, being not deep, has the advantage of being less 
computationnally intensive. FCN is a first attempt of applying "deep 
feature" representations to the task of semantic segmentation. This 
archicture has the advantage of re-using a classical deep learning 
architecture with added on upsampling layer and skip layers. The 
upsampling layers enable the network to learn a pixel level classification 
and the skip layers enable the network to fuse different levels of 
abstraction to the final prediction. This model can be fine tuned with a 
set of pretrained-weights extracted from the classical deep learning 
architecture. DeconvNet is also based on a classical architecture, 
however, in this network their are no skip layer as one intends to learn 
the proper upsampling threw repeated deconvolution and convolution 
layers. This model can also be fine tuned.
\section{Result}
\label{sec:result}
table of values
\section{Discussion}
\label{sec:discussion}
What's next?

>>>>

\section{Related work}
\label{sec:related}
Image segmentation and object recognition in medical imagining have 
been tackled for many years and many approaches have been found. 
Methods based on mathematical morphological operators have been 
widely used and applied for segmentation and feature extraction, 
however such methods rely on the user to manually define the 
information that is relevant for his task \cite{irshad2014methods}. 
Segmentation methods based on a strong priori information are also 
possible and yield comparable results in terms of accuracy, in 
\cite{ranefall2016fast} they segment the picture using a ellispe fit 
which is considerably faster than other state of the art methods. Graph-
based tools for segmentation are also possible in histopathology 
\cite{ta2009graph}. \cite{manivannanlocal} focus on gland 
segmentation, they achieve good results by predicting image patches as 
a whole, via a classification scheme. The output confidence vector is 
then preprocessed to obtain the final segmentation. Alternative methods 
have arisen from the achieving Convolutional neural networks 
\cite{lecun}, in particular strong incentive rose with the very impressive 
results that they achieved in the pascal voc challenge with 
\cite{ImageNet}. Recent advances in deep neural network, and in 
particular in their optimization have made them become the state-of-the-
art model for object recognition.  Deep neural network have also been 
used for different task and have yielded very impressiv results, we can think of 
semantic segmentation problems, where \cite{long2015fcn} use "de-
convolution layers" and up-sampling in order to identify and precisely 
locate objects within a picture. Different architecture arising from 
different intuition are also possible and have been applied in this paper
Talk about related work.

\section{DataSet}
\label{sec:dataset}

%% Contribution as a dataset, small introduction
One of the main contributions of this paper is the now public available 
nuclei detection dataset within HE stainned histopathology images which 
can be found at website %\url{www.cbio.ensmp.fr:/pnaylor/download/dataset.zip} 
(not a true address). This annotated dataset provides images clustered by 
patients. Each patient has at least 3 annotated $512 \times 512$ HE 
stainned histopathology images with their associated ground truth. Each 
ground truth image is a $512 \times 512$ where each pixel value above 
$0$ is considered as a pixel belonging to a nuclei. The differences in 
values of these pixels denote different nucleus, such an annotation can 
be used in several processing step which does or doesn't take into 
account clutered nuclei. See figure \ref{fig:annotation} for an example of 
three annotated images. This annotation was conducted via the help of 
the software ITK-snap and were annotated by the authors of the paper.

@@

%%Data set description 
In this data set we have annotated a considerous amount of cells, 
including normal breast cells (epithelial and lobule cells),  cancerous 
breast cells, fibroblasts,  endothelial cells, fat cells, macrophage cells and 
inflammatory cells (lymphocytes and plasmocytes). For the moment, cell types have not been seperated, which means that in this dataset every annotation corresponds to a global type of cell.

\begin{itemize}
\item Number of images: 33 \\
\item Number  of cells: 2754 \\
\item Maximum number of cells in one sample: 293 \\
\item Minimum number of cells in one sample: 5 \\
\item Mean number of cells: 83 \\
\item Standard deviation of number of cells: 63 \\
\end{itemize}

@@

%% Data augmentation and Hyper parameter training: Training scheme
%% Check number of images and number of transformations
To train our models, as the number of available annotated is scarse, we 
used a great number of transformation for the data augmentation. From 
a original size of 33 annotated images, adding flips, rotations, bluriness 
and random elastic deformations enabled us to have more then 
$400 000$ training images. 
We also try out several hyperparameter configurations: the learning rate and 
momentum for the stochastic gradient descent, the weight decay value.  
In practice, we found that hyperparameters tuning didn't influence the 
scores much, the exepction being the learning rate. If the learning rate 
was not of the right magnitude the given network did not seem to learn. 
We also experienced with different 
initialization value and if possible, we also considered pretrained layers. 
Using pretrained layers made learning more efficient and made score 
values more robust.

\section{Different architectures/Results}
\label{sec:method}
We experience with 4 known arhitectures in semantic segmentation, one 
will be named BaochuanNet, Fully Convolutionnal Net (FCN), DeconvNet, 
UNet. The most basic architecture, BaochuanNet, consists of 4 
convolutionnal layer where each convolutionnal layer has 8 feature map. 
This net, being not deep, has the advantage of being less 
computationnally intensive. FCN is a first attempt of applying "deep 
feature" representations to the task of semantic segmentation. This 
archicture has the advantage of re-using a classical deep learning 
architecture with added on upsampling layer and skip layers. The 
upsampling layers enable the network to learn a pixel level classification 
and the skip layers enable the network to fuse different levels of 
abstraction to the final prediction. This model can be fine tuned with a 
set of pretrained-weights extracted from the classical deep learning 
architecture. DeconvNet is also based on a classical architecture, 
however, in this network their are no skip layer as one intends to learn 
the proper upsampling threw repeated deconvolution and convolution 
layers. This model can also be fine tuned. The final architecture that we tried is the UNet. This network combines both contribution of the above networks, the UNet has a similar architecture to the DeconvNet with skip layers.
\section{Result}
\label{sec:result}

\begin{tabular}{|c|c|c|c|c|c|}
 & UNet & Baochuan & DeconvNet & FCN & Ensemble \\
%\hrule
Accuracy          &       0.89 &       0.94 & 0.97\\
IU   &       0.70 &       0.76 &     0.86 \\
Recall                     &       0.75 &       0.74  &     0.86 &&\\
Precision                  &       0.64 &       0.74 &     0.86 &&\\
F1                         &       0.69 &       0.74 &     0.86 &&  \\
TP             &       0.75 &       0.74 &     0.86 && \\
TN             &       0.92 &       0.96 &     0.98 &&\\
Performance                &       0.84 &       0.85 &     0.92 &&\\
Pixel error                &       0.11 &       0.06 &     0.03 &&\\
\end{tabular}

\section{Discussion}
\label{sec:discussion}
What's next?
